Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalnew\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-06-22 ms.tex
changed numbers
updated numbers

\newcommand{\Nfp}{7}
\newcommand{\Nvalidated}{19}
\newcommand{\Nlimbo}{9} %adds up to 36
\newcommand{\Nvalnew}{16} % 4 previously validated

@@

We have presented stellar parameters for all planet candidates systems identified by
\paperit.
We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
identify \Nfp\ as false positives.
Of these planets, 3 have been previously validated in other works, while \Nvalnew\ are
validated here for the first time.
The systems not validated as planets or false positives remain as planet candidates.

>>>>

\newcommand{\Nfp}{6}
\newcommand{\Nvalidated}{21}
\newcommand{\Nlimbo}{9} %adds up to 36
\newcommand{\Nvalnew}{17} % 4 previously validated

@@

We have presented stellar parameters for all planet candidates systems identified by
\paperit.
We statistically validate \Nvalidated\ of the 36 candidates as bona fide planets, and we
identify \Nfp\ as false positives, including two systematic false alarms.
Of the planets, 4 have been previously validated in other works, while \Nvalnew\ are
validated here for the first time.
The systems not validated as planets or false positives remain as planet candidates.
